Agents and you, a brief summary

### 2015-10-28 agents/summery.tex
added the update transition and comments.

\section{Markov}

>>>>

\subsection{Transitions}
Execution of a belief update action $\alpha$ modifies the belief and goal
bases. $Update$ is an update function that is specified by the believe
update actions and $\gamma'=\gamma - \{\psi \in \gamma | \sigma' \vDash \psi\}$.
Which basically says that $\gamma'$ is equal to $\gamma$ minus the update.

\begin{prooftree}
	\AxiomC{$Update(\sigma, \alpha\theta)=\sigma'$}
	\UnaryInfC{$\langle i, \sigma, \gamma, \{(\alpha,id)\}, \theta, 
		\xi\rangle \to 
	\langle \langle i, \sigma', \gamma', \{\}, \theta, \xi\rangle$}

\end{prooftree}
\section{Markov}
